Relationships in the extremes and their influence on competition and coexistence

### 2022-04-14 paper/Paper.Rnw
fix typo

%Also need to talk about how this stuff will apply to data.
As an introductory investigation of ATAs within the framework of MCT, 
we used simple and extreme examples, and future work should assess more complex relationships, systems, and models. 
In our theoretical exploration, we implemented a simple lottery model and assessed 
the influence of extremely asymmetric associated noise, i.e., the noise was perfectly correlated
in exactly one half of the distribution. However, more complex models (such as structured demographic models
or integral projection models should be explored )and varying degrees and qualities of ATA, (copula parameters, 
difference between tails, rate of relatedness(slope of expansion??) should be implemented and explored.
Moreover, because our empirical application makes use of a simple and controlled lab system, future studies
should be done to assess the extent of how much ATAs are important for complex systems and field systems which are 
often subject to factors beyond our control.
Because modeling the dynamics of long-lived populations can be challenging, a good field system to start
exploring the ideas presented here is a system of annual plants. 
For example, the ATAs effcts of rainfall timing on the coexistence of grasses and forbs 
in California grasslands \citep{Hallett_2019} could be a fruitful 
further investigation of biodiversity maintenance in California grasslands and the effects of extreme 
rainfall fluctuation given the highly variable climate of the area.
Moreover, our approach may provide more insight when expanded to consider fluctuations across space,
in regards to questions about population synchrony, Moran effects, and the suggestion of possible ATA specialists.

>>>>

%Also need to talk about how this stuff will apply to data.
As an introductory investigation of ATAs within the framework of MCT, 
we used simple and extreme examples, and future work should assess more complex relationships, systems, and models. 
In our theoretical exploration, we implemented a simple lottery model and assessed 
the influence of extremely asymmetric associated noise, i.e., the noise was perfectly correlated
in exactly one half of the distribution. However, more complex models (such as structured demographic models
or integral projection models should be explored )and varying degrees and qualities of ATA, (copula parameters, 
difference between tails, rate of relatedness(slope of expansion??) should be implemented and explored.
Moreover, because our empirical application makes use of a simple and controlled lab system, future studies
should be done to assess the extent of how much ATAs are important for complex systems and field systems which are 
often subject to factors beyond our control.
Because modeling the dynamics of long-lived populations can be challenging, a good field system to start
exploring the ideas presented here is a system of annual plants. 
For example, the ATAs effects of rainfall timing on the coexistence of grasses and forbs 
in California grasslands \citep{Hallett_2019} could be a fruitful 
further investigation of biodiversity maintenance in California grasslands and the effects of extreme 
rainfall fluctuation given the highly variable climate of the area.
Moreover, our approach may provide more insight when expanded to consider fluctuations across space,
in regards to questions about population synchrony, Moran effects, and the suggestion of possible ATA specialists.
